Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-09 draft/accordionComplexSurfaces.tex
References to OPS.

@@

\pierreguy{Remark on the comparison with the surface of OPS}

>>>>

The following proposition appears in \cite[Proposition 1.25]{OpperPlamondonSchroll}.

@@

\begin{remark}
\label{rem:comparisonWithOPS}
The construction of the surface given in Definition \ref{def:surfaceQuiver} yields the same surface as the one constructed in \cite{OpperPlamondonSchroll}.
A notable difference is that in \cite{OpperPlamondonSchroll}, only~$\dissection_{\bar Q}$ is given, and~$\dissection_{\bar Q}\dual$ is deduced (it is called the dual lamination).
Another minor difference is that the construction in \cite{OpperPlamondonSchroll} is written only for gentle algebras, while here it is generalized to locally gentle algebras.

The major difference with \cite{OpperPlamondonSchroll} is the application of the surface of a (locally) gentle algebra: 
there, it is used as a model for the derived category of the gentle algebra (graded arcs correspond to indecomposable objects in that category),
while here, it will be used as a model for walks in~$\bar Q$ ($\dissection_{\bar Q}$-accordions will correspond to walks in~$\bar{Q}$, see Proposition \ref{prop:walks=arcs}).
\end{remark}
